Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
???

To implement the integration on $\Ball{R}{\vx} \cap \Shape$
(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all digital
points inside such domain (Fig.~\ref{fig:approx}-$b$) and then to estimate the
geometrical moment as the sum of the geometrical moments of each elementary
cubes lying in the intersection. On GPU, \emph{mipmap} textures are used to
obtain a multi-resolution information: if the input binary object is stored in a
3D texture, GPU hardware can construct a multi-resolution pyramid such that 8
neighboring voxel intensities at level $l$ are averaged to define the voxel
value at level $l+1$. If the level 0 corresponds to the binary input object, at
a given level $l$, a voxel $(x,y,z)$ contains the fraction of $\DSh$ belonging
to the cube of center $(x,y,z)$ and edge length $2^l$. As a consequence, we can
approximate the volume of $\Ball{R}{\vx}\cap\Shape$ by considering mipmap values
at a given resolution $l$ (Fig.~\ref{fig:approx}-$c$). In this case, errors only
occurs for cells lying inside $\Shape$ (with density 1) not entirely covered by
$\Ball{R}{\vx}$. Furthermore, the \emph{mipmap} texture can be used to design,
using a single texture probe, a fast inclusion test of a given cell $c$ at level
$l$ into the shapes: we say that $c$ is in $\Shape$ if its density (retrieved
from the texture probe at level $l$) is greater than $1/2$. The idea here is to
mimic a lend of adaptive Gauss digitization process.

@@

Then, we compare the approximation made by computing curvature from level $l >
l_0$ in order to accelerate visualization with the ground truth result obtained
at level $l_0$. We also compare them with the hierarchical algorithm discussed
in Section~\ref{sec:hierarchical}. The results are presented in
Table~\ref{tab:full-res-stat}, and illustrated in Figure~\ref{fig:refine}.

We can first see that the number of texel fetch required to compute
the curvature reduces drastically when computing the approximations.
This is mandatory if we want to increase the framerate.
However, we can also note that the error increases quite slowly.
The errors obtained comparing $l_1$, or for bigger radii $l_2$ approximations
with the $l_0$ level are small. The errors measured comparing higher levels
are of course much bigger and those level are thus never used in practice.
They are presented here to illustrate how the refining process converges to
the $l_0$ level. Thanks to this low error, higher approximation levels are visually
very similar to the $l_0$ level. We can therefore use them for exploring our
datasets in real time, changing the radii on the fly and visualizing dynamic datasets.

@@

     \end{tikzpicture}
     \end{center}
  \caption{Timings obtained while visualizing an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm.
  Orange is the required time to extract the triangulation, and blue are the curvature computations from level $l_4$ (light blue) to level $l_0$ (dark blue).
  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$), with different radii ($8$, $10$, $16$ and $20$)}
  \label{fig:timings}
\end{figure}

@@

\subsection{Visualisation}

For dynamic datasets, we consider a time varying implicit
surface. Since it would have been to expensive to update the a mipmap texture
of densities at each time step, we simply evaluate the implicit
expression at each vertex of a cell to decide if such cell is included
or not into $\Ball{R}{\vx}\cap \Shape$.
\todo[inline]{blabla experiments}

>>>>

To implement the integration on $\Ball{R}{\vx} \cap \Shape$
(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all digital
points inside such domain (Fig.~\ref{fig:approx}-$b$) and then to estimate the
geometrical moment as the sum of the geometrical moments of each elementary
cubes lying in the intersection. On GPU, \emph{mipmap} textures are used to
obtain a multi-resolution information: if the input binary object is stored in a
3D texture, GPU hardware can construct a multi-resolution pyramid such that 8
neighboring voxel intensities at level $l$ are averaged to define the voxel
value at level $l+1$. If the level 0 corresponds to the binary input object, at
a given level $l$, a voxel $(x,y,z)$ contains the fraction of $\DSh$ belonging
to the cube of center $(x,y,z)$ and edge length $2^l$. As a consequence, we can
approximate the volume of $\Ball{R}{\vx}\cap\Shape$ by considering mipmap values
at a given resolution $l$ (Fig.~\ref{fig:approx}-$c$). In this case, errors only
occurs for cells lying inside $\Shape$ (with density 1) not entirely covered by
$\Ball{R}{\vx}$. Furthermore, the \emph{mipmap} texture can be used to design,
using a single texture probe, a fast inclusion test of a given cell $c$ at level
$l$ into the shapes: we say that $c$ is in $\Shape$ if its density (retrieved
from the texture probe at level l) is greater than $1/2$. The idea here is to
mimic a lend of adaptive Gauss digitization process.

@@

Then, we compare the approximation made by computing curvature from level $l >
l_0$ in order to accelerate visualisation with the ground truth result obtained
at level $l_0$. We also compare them with the hierarchical algorithm discussed
in Section~\ref{sec:hierarchical}. The results are presented in
Table~\ref{tab:full-res-stat}, and illustrated in Figure~\ref{fig:refine}.

We can first see that the number of texel fetch required to compute
the curvature reduces drastically when computing the approximations.
This is mandatory if we want to increase the framerate.
However, we can also note that the error increases quite slowly. 
The errors obtained comparing $l_1$, or for bigger radii $l_2$ approximations
with the $l_0$ level are small. The errors measured comparing higher levels
are of course much bigger and those level are thus never used in practice.
They are presented here to illustrate how the refining process converges to 
the $l_0$ level.
Thanks to this low error, higher approximation levels are visually 
very similar to the $l_0$ level. We can therefore use them for exploring our 
datasets in real time, changing the radii on the fly and visualising dynamic datasets.

@@

     \end{tikzpicture}
     \end{center}
  \caption{Timings obtained while visualising an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm. 		
  Orange is the required time to extract the triangulation, and blue are the curvature computations from level $l_4$ (light blue) to level $l_0$ (drak blue).
  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$), with different radii (8, 10, 16, 20)}
  \label{fig:timings}
\end{figure}

@@

%\subsection{Visualisation}
%
%For dynamic datasets, we consider a time varying implicit
%surface. Since it would have been to expensive to update the a mipmap texture
%of densities at each time step, we simply evaluate the implicit
%expression at each vertex of a cell to decide if such cell is included
%or not into $\Ball{R}{\vx}\cap \Shape$.
%\todo[inline]{blabla experiments}
